---
title: |
  ![](r-project.svg){width=1in}Data Mining
author: "Ru"
date: "2023-06-15"
output: flexdashboard::flex_dashboard
source_code: embed
---


```{r setup, include=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
library(reshape2)
library(lubridate)
library(arules)
library(arulesViz)

predelete_dataset <- read_excel("C:/Users/user/Desktop/DG&IR/imdb_movies.xlsx","imdb_movies_adj")
dataset <- predelete_dataset[complete.cases(predelete_dataset), ]
#1895-1927movie
beg_dataset <- dataset %>%  filter(year(date_x)<1927 & year(date_x)>=1895)
#1927-1960movie
mid_dataset <- dataset %>%  filter(year(date_x)<1960 & year(date_x)>=1927)
#1960-1980movie
midlate_dataset <- dataset %>%  filter(year(date_x)<1980 & year(date_x)>=1960)
#1980-movie
recent_dataset <- dataset %>%  filter(year(date_x)<=2023 & year(date_x)>=1980)

asso_beg_dataset <- beg_dataset
asso_beg_dataset$date_x <- format(asso_beg_dataset$date_x, "%Y-%m-%d")
asso_beg_dataset$date_x <- 'Early'
#summary(asso_beg_dataset$revenue)
for (i in 1:nrow(asso_beg_dataset)) {
  if (asso_beg_dataset$revenue[i] >= 4.164e+08) {
    asso_beg_dataset$revenue[i] <- "High"
  }else if (asso_beg_dataset$revenue[i] >= 2.517e+08){
    asso_beg_dataset$revenue[i] <- "Normal"
  }else{
    asso_beg_dataset$revenue[i] <- "Low"
  }
}
asso_beg_dataset_apr <- data.frame(date=factor(asso_beg_dataset$date_x),
                                   genre=factor(asso_beg_dataset$genre),
                                   revenue=factor(asso_beg_dataset$revenue))


asso_mid_dataset <- mid_dataset
asso_mid_dataset$date_x <- format(asso_mid_dataset$date_x, "%Y-%m-%d")
asso_mid_dataset$date_x <- 'Middle'
for (i in 1:nrow(asso_mid_dataset)) {
  if (asso_mid_dataset$revenue[i] >= 4.164e+08) {
    asso_mid_dataset$revenue[i] <- "High"
  }else if (asso_mid_dataset$revenue[i] >= 2.517e+08){
    asso_mid_dataset$revenue[i] <- "Normal"
  }else{
    asso_mid_dataset$revenue[i] <- "Low"
  }
}
asso_mid_dataset_apr <- data.frame(date=factor(asso_mid_dataset$date_x),
                                   genre=factor(asso_mid_dataset$genre),
                                   revenue=factor(asso_mid_dataset$revenue))


asso_midlate_dataset <- midlate_dataset
asso_midlate_dataset$date_x <- format(asso_midlate_dataset$date_x, "%Y-%m-%d")
asso_midlate_dataset$date_x <- 'Middle Late'
for (i in 1:nrow(asso_midlate_dataset)) {
  if (asso_midlate_dataset$revenue[i] >= 4.164e+08) {
    asso_midlate_dataset$revenue[i] <- "High"
  }else if (asso_midlate_dataset$revenue[i] >= 2.517e+08){
    asso_midlate_dataset$revenue[i] <- "Normal"
  }else{
    asso_midlate_dataset$revenue[i] <- "Low"
  }
}
asso_midlate_dataset_apr <- data.frame(date=factor(asso_midlate_dataset$date_x),
                                   genre=factor(asso_midlate_dataset$genre),
                                   revenue=factor(asso_midlate_dataset$revenue))


asso_recent_dataset <- recent_dataset
asso_recent_dataset$date_x <- format(asso_recent_dataset$date_x, "%Y-%m-%d")
asso_recent_dataset$date_x <- 'Recent'
for (i in 1:nrow(asso_recent_dataset)) {
  if (asso_recent_dataset$revenue[i] >= 4.164e+08) {
    asso_recent_dataset$revenue[i] <- "High"
  }else if (asso_recent_dataset$revenue[i] >= 2.517e+08){
    asso_recent_dataset$revenue[i] <- "Normal"
  }else{
    asso_recent_dataset$revenue[i] <- "Low"
  }
}
asso_recent_dataset_apr <- data.frame(date=factor(asso_recent_dataset$date_x),
                                       genre=factor(asso_recent_dataset$genre),
                                       revenue=factor(asso_recent_dataset$revenue))





asso_dataset <- rbind(asso_beg_dataset, asso_mid_dataset, asso_midlate_dataset, asso_recent_dataset)
for (i in 1:nrow(asso_dataset)) {
  if (asso_dataset$revenue[i] >= 4.164e+08) {
    asso_dataset$revenue[i] <- "High"
  }else if (asso_dataset$revenue[i] >= 2.517e+08){
    asso_dataset$revenue[i] <- "Normal"
  }else{
    asso_dataset$revenue[i] <- "Low"
  }
}

asso_dataset_apr <- data.frame(date=factor(asso_dataset$date_x),
                               genre=factor(asso_dataset$genre),
                               revenue=factor(asso_dataset$revenue))



# Get the counts of each genre
genre_counts <- data.frame(dataset$genre)

# Get the unique genres with non-zero counts and select the top 10 genres
top_genres_count <- genre_counts %>% 
  group_by(dataset.genre) %>% 
  summarise(Count_t=n()) %>% 
  arrange(desc(Count_t)) %>%
  head(10)

# Create a data frame with genre names and their corresponding explode values
data <- data.frame(genre = top_genres_count$dataset.genre, count = top_genres_count$Count_t)
data$percentage <- (data$count / sum(data$count)) * 100

movie_years <- dataset %>%
  mutate(year = lubridate::year(date_x)) %>%
  count(year) %>%
  arrange(year)

movie_counts <- table(format(dataset$date_x, "%Y"))

# Convert the table to a data frame and sort by year
movie_counts <- data.frame(Year = as.numeric(names(movie_counts)),
                           Count = as.numeric(movie_counts))
movie_counts <- movie_counts[order(movie_counts$Year), ]

# Calculate the correlation matrix
cor_matrix <- cor(dataset[c("revenue", "score", "budget_x")])
early_cor_matrix <- cor(beg_dataset[c("revenue", "score", "budget_x")])
mid_cor_matrix <- cor(mid_dataset[c("revenue", "score", "budget_x")])
midlate_cor_matrix <- cor(midlate_dataset[c("revenue", "score", "budget_x")])
recent_cor_matrix <- cor(recent_dataset[c("revenue", "score", "budget_x")])


# Sort the data frame by revenue in ascending order and take top 20
Movies_sorted <- dataset[order(dataset$revenue), ]
top_20_revenues <- tail(Movies_sorted, 20)

# asso
transaction <- transactions(asso_beg_dataset_apr)

early_rule <- apriori(transaction,
                parameter=list(support=0.1,
                               confidence=0.5,
                               minlen=3),
                appearance = list(default="lhs",
                                  rhs=c("revenue=High", "revenue=Normal","revenue=Low"))
)

transaction <- transactions(asso_mid_dataset_apr)

middle_rule <- apriori(transaction,
                parameter=list(support=0.02,
                               confidence=0.5,
                               minlen=3),
                appearance = list(default="lhs",
                                  rhs=c("revenue=High", "revenue=Normal","revenue=Low"))
)

transaction <- transactions(asso_midlate_dataset_apr)

midlate_rule <- apriori(transaction,
                parameter=list(support=0.005,
                               confidence=0.5,
                               minlen=3),
                appearance = list(default="lhs",
                                  rhs=c("revenue=High", "revenue=Normal","revenue=Low"))
)

transaction <- transactions(asso_recent_dataset_apr)

recent_rule <- apriori(transaction,
                parameter=list(support=0.001,
                               confidence=0.5,
                               minlen=3),
                appearance = list(default="lhs",
                                  rhs=c("revenue=High", "revenue=Normal","revenue=Low"))
)




```

Introduction of overall dataset
=======================================================================
Row {.tabset .tabset-fade}
-------------------------------------

### line chart about movies produced
```{r}

ggplot(movie_counts, aes(x = Year, y = Count)) +
  geom_line(color = "red", size = 1.8) +
  labs(title = "Movies Produced per Year Since 1903-2023") +
  annotate("rect", xmin = 1895, xmax = 1927, ymin = -Inf, ymax = Inf, fill = "#81C0C0", alpha = 0.3)+
  annotate("rect", xmin = 1927, xmax = 1960, ymin = -Inf, ymax = Inf, fill = "#9999CC", alpha = 0.3)+
  annotate("rect", xmin = 1960, xmax = 1980, ymin = -Inf, ymax = Inf, fill = "#C48888", alpha = 0.3)+
  annotate("rect", xmin = 1980, xmax = 2023, ymin = -Inf, ymax = Inf, fill = "#ADADAD", alpha = 0.3)+
  theme_minimal()

```

### bar plot of top 20 movie revenues since 1903-2023
```{r}

ggplot(top_20_revenues, aes(x = reorder(names, revenue), y = revenue)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  labs(title = "Top 20 Movie Revenues", x = "Movie Title", y = "Revenue") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```


### pie chart of top 10 genres of movies
```{r}

ggplot(data, aes(x = "", y = percentage, fill = genre)) +
  geom_col(width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Top 10 Genre of Movies Since 1903-2023") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), position = position_stack(vjust = 0.5)) +
  guides(fill = guide_legend(title = "Category"))

```

Correlation of overall data
=======================================================================

### Heatmap of correlation between Revenue vs Score vs Budget
```{r}

ggplot(melt(cor_matrix), aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white", "blue")) +
  geom_text(aes(Var2, Var1, label = value), size = 3) +
  labs(title = "Correlation between Revenue vs Score vs Budget") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


Correlation of each period data
=======================================================================

Row
-------------------------------------
    
### Heatmap of correlation between Revenue vs Score vs Budget(1895-1927)
```{r}
ggplot(melt(early_cor_matrix), aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white", "blue")) +
  geom_text(aes(Var2, Var1, label = value), size = 3) +
  labs(title = "Correlation between Revenue vs Score vs Budget") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Heatmap of correlation between Revenue vs Score vs Budget(1927-1960)
```{r}

ggplot(melt(mid_cor_matrix), aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white", "blue")) +
  geom_text(aes(Var2, Var1, label = value), size = 3) +
  labs(title = "Correlation between Revenue vs Score vs Budget") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
   
Row 
-------------------------------------
 
### Heatmap of correlation between Revenue vs Score vs Budget(1960-1980)
```{r}

ggplot(melt(midlate_cor_matrix), aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white", "blue")) +
  geom_text(aes(Var2, Var1, label = value), size = 3) +
  labs(title = "Correlation between Revenue vs Score vs Budget") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Heatmap of correlation between Revenue vs Score vs Budget(1980-2023)
```{r}

ggplot(melt(recent_cor_matrix), aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradientn(colours = c("white", "blue")) +
  geom_text(aes(Var2, Var1, label = value), size = 3) +
  labs(title = "Correlation between Revenue vs Score vs Budget") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



Association between period, genres and revenue (1895-1927) 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------
    
### Association map in early data
```{r}

plot(head(sort(early_rule,
               by="lift"),
          n=10),
     method="graph",
     engine="htmlwidget")
```

### Association inspect in early data

```{r}

inspect(head(sort(early_rule,by="lift"),10))

```

Association between period, genres and revenue (1927-1960) 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### Association map in maiddle data
```{r}

plot(head(sort(middle_rule,
               by="lift"),
          n=10),
     method="graph",
     engine="htmlwidget")

```
 
### Association inspect in maiddle data
```{r}

inspect(head(sort(middle_rule,by="lift"),10))

```


Association between period, genres and revenue (1960-1980) 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### Association map in maiddle-late data
```{r}


plot(head(sort(midlate_rule,
               by="lift"),
          n=10),
     method="graph",
     engine="htmlwidget")

```
 
### Association inspect in maiddle-late data
```{r}

inspect(head(sort(midlate_rule,by="lift"),10))

```


Association between period, genres and revenue (1980-2023) 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### Association map in recent data
```{r}

plot(head(sort(recent_rule,
               by="lift"),
          n=10),
     method="graph",
     engine="htmlwidget")
```
 
### Association inspect in recent data
```{r}

inspect(head(sort(recent_rule,by="lift"),10))

```

